Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2022-03-09 authors_responses/conditional_accept/authors_response.tex
Some errors in equations fixed (missing '2', notation update, etc) Reviewer 2 comments finished and more responses to reviewer 3 added. Relevant changes to main text made as well

It is hard to say explicitly whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet). In addition, a further optimised implementation executed on more powerful hardware could result in significantly faster runtimes.

\textit{+changes made} time was used primarily as a comparitive measure in key sizes.

@@

@@

@@

In practice, chosen cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key. For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must not be leaked for the foreseeable future. Since cryptographic \textit{guarantees} are required, computation is not directly considered when choosing key sizes. However, in cases where computation makes desired cryptograhpic guarantees infeasible, shorter required secrecy or more frequent key exchanges can be considered to reduce key sizes and computation times.

\textit{+changes made}

>>>>

It is hard to explicitly say whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet). In terms of reducing this time, a smaller key size, optimised code or more powerful hardware could be used depending on the scenario. We have updated the discussion on execution time and choosing key sizes in section VI to elaborate on their relation and how computation time could be reduced in hopes it makes the reasoning clearer.

@@

My response.
existing typical schemes AES and RSA

@@

As the proposed method presents a solution to a novel cryptographic problem

due to the lack of methods to which it can be comap

as the work presents a novel solution to a cryptographic problem
in addition to keeping the work short
the divide .. would further complicate the interpretation of complexity analysis statements due to the combination of bit terms and number terms
Due to the divide between the cryptographic component and the localisation component

We hope this reasoning 
backs the reasoning for excluding a complexity analysis in the work

@@

In practice, choosing a cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key. For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must remain private for the foreseeable future. Since the secrecy is required, computation is not directly considered when choosing key sizes. However, in cases where computation makes the desired secrecy infeasible, shorter required secrecy and more frequent key exchanges can be considered to reduce key sizes and computation times. To elaborate this requirement, we have added comments discussing the execution time and choosing key sizes in section VI.

### 2022-03-09 main.tex
Some errors in equations fixed (missing '2', notation update, etc) Reviewer 2 comments finished and more responses to reviewer 3 added. Relevant changes to main text made as well

Key generation is computed by first choosing two equal-length and sufficiently large primes $p$ and $q$, and computing $N=pq$. A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,i\in\{1,\dots,n\}$, uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

When all encryptions $c^{(t)}_{i},\,i\in\{1,\dots,n\}$ are sent to the aggregator, summation and decryption of the aggregated sum are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N} \pmod{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}(N+1)^{a_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
    \end{split}
\end{equation*}
removing all noise terms.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal-length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

@@

The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root. Similarly, the Jacobian of $h_i$ at $\hat{\vec{x}}_{k|k-1}$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\hat{x}_{k|k-1} - s_{x,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        0 \\
        \vdots
    \end{bmatrix}\,,
\end{equation}
cannot be either. We, therefore, consider the modified measurement functions
\begin{equation}
    h'_i(\vec{x}) = h_i(\vec{x})^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\hat{\vec{x}}_{k|k-1}$, as
\begin{equation}
    \begin{split}
        h'_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (x - s_{x,i})^2 + (y - s_{y,i})^2 \\
        &= x^2 + y^2 -2s_{x,i}x -2s_{y,i}y +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\hat{x}_{k|k-1} - 2s_{x,i} \\
        2\hat{y}_{k|k-1} - 2s_{y,i} \\
        0 \\
        \vdots
    \end{bmatrix}\,. \label{eqn:modified_jacobian}
\end{equation}
Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $\hat{x}_{k|k-1}^2$, $\hat{y}_{k|k-1}^2$, $\hat{x}_{k|k-1}$ and $\hat{y}_{k|k-1}$. To show how the corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be similarly rearranged and used for localisation, we also require the existence of measurements following a modified measurement model of the form
\begin{equation}
    z'_{k,i} = h'_i(\vec{x}_k)+v'_{k,i}\,, \label{eqn:modified_measurement_model}
\end{equation}
where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r'_{k,i}$.

@@

        &\quad+ (-r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\

@@

    \State Let $\bm{\alpha}_{i}^{(k,\tau)}$ represent the encryption of $\alpha_{i}^{(k,\tau)}$ in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb}
    \State $\bm{\alpha}_{i}^{(k,1)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{\prime-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\bm{\alpha}_{i}^{(k,\tau)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$\tau \gets 1$ to $6$}
        \State Send $\bm{\alpha}_{i}^{(k,\tau)}$ to the navigator
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

In addition to filter error, computational performance is important to consider when relying on cryptographic methods. Figure \ref{fig:sim_timing} shows the averages of $10$ execution times when varying the numbers of sensors and key sizes (bit lengths of $N$). Here, increasing the number of sensors primarily affected the number of inter-process communications and aggregation modular multiplications due to the asynchronous implementation.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/timing.pdf}
    \caption{Runtimes for varying key sizes and numbers of sensors.}
    \label{fig:sim_timing}
\end{figure}
We can see from the figure that the predominant computational costs stem from cryptographic computations and are directly dependent on the chosen key size. The key size should be chosen such that sufficient security is achieved, and the current recommendation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}. For our implementation of the filter, run on the aforementioned hardware, this results in a filter update computation duration of roughly $1.7s$.

>>>>

Key generation is computed by first choosing two equal-length and sufficiently large primes $p$ and $q$, and computing $N=pq$. A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,i\in\{1,\dots,n\}$, uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i\,,
\end{equation}
and sent to the aggregator.

@@

When all encryptions $c^{(t)}_{i},\,i\in\{1,\dots,n\}$ are sent to the aggregator, summation and decryption of the aggregated sum are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N} \pmod{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}(N+1)^{a^{(t)}_{i}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a^{(t)}_{i}} \pmod{N^2}\,,
    \end{split}
\end{equation*}
removing all noise terms.

@@

As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$. To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal-length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i$.

@@

The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root. Similarly, the Jacobian of $h_i$ at $\hat{\vec{x}}_{k|k-1}$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\hat{x}_{k|k-1} - s_{x,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
        0 \\
        \vdots
    \end{bmatrix}^\top\,,
\end{equation}
cannot be either. We, therefore, consider the modified measurement functions
\begin{equation}
    h'_i(\vec{x}) = h_i(\vec{x})^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\hat{\vec{x}}_{k|k-1}$, as
\begin{equation}
    \begin{split}
        h'_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (x - s_{x,i})^2 + (y - s_{y,i})^2 \\
        &= x^2 + y^2 -2s_{x,i}x -2s_{y,i}y +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\hat{x}_{k|k-1} - 2s_{x,i} \\
        2\hat{y}_{k|k-1} - 2s_{y,i} \\
        0 \\
        \vdots
    \end{bmatrix}^\top\,. \label{eqn:modified_jacobian}
\end{equation}
Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $\hat{x}_{k|k-1}^2$, $\hat{y}_{k|k-1}^2$, $\hat{x}_{k|k-1}$ and $\hat{y}_{k|k-1}$. To show how the corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be similarly rearranged and used for localisation, we also require the existence of measurements following a modified measurement model of the form
\begin{equation}
    z'_{k,i} = h'_i(\vec{x}_k)+v'_{k,i}\,, \label{eqn:modified_measurement_model}
\end{equation}
where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r'_{k,i}$.

@@

        &\quad+ (-2r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\

@@

    \State Let $\bm{\alpha}_{i}^{(k,\tau)}$ represent the encryption of $\alpha_{i}^{(k,\tau)}$ in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb}
    \State $\bm{\alpha}_{i}^{(k,1)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1}z_{k,i}')}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}^3)}
    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2)}\cdot$\par
    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{\prime-1}s_{x,i}z_{k,i}')}
    H(k\mathbin\|1)\pmod{N^2}$
    \State Compute remaining $\bm{\alpha}_{i}^{(k,\tau)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
    \For{$\tau \gets 1$ to $6$}
        \State Send $\bm{\alpha}_{i}^{(k,\tau)}$ to the navigator
    \EndFor
    \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

In addition to filter error, computational performance is important to consider when relying on cryptographic methods. Figure \ref{fig:sim_timing} shows the averages of $10$ execution times when varying the numbers of sensors and key sizes (bit lengths of $N$). Here, increasing the number of sensors primarily affects the number of inter-process communications and aggregation steps due to the asynchronous implementation.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/timing.pdf}
    \caption{Runtimes for varying key sizes and numbers of sensors.}
    \label{fig:sim_timing}
\end{figure}
We can see that the predominant computational costs stem from cryptographic computations and are directly dependent on the chosen key size. In practice, choosing a key size should take into account the duration of secrecy and the secret key lifetime. When relying on the DCRA for security, the current recommendation for encrypting government documents is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}. For our implementation and aforementioned hardware, this results in a filter update roughly every $1.7s$. In a scenario where sensors are mobile and past navigations can be made public, reduced key sizes can be considered, while a further decrease in computation time could be achieved with code optimisations and more powerful hardware.
